I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-18 Paper/proofs.tex
update proof

				In this section, we will prove theorem \ref{th2}. We will prove that theorem by proving the following theorem:

@@

					Using MILP method, if every nodes $b$ in any compensating pair
					$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
					bounds computed by MILP are the exact maximal and minimal value of $z$.
				\end{theorem}

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be on a weak compensating pair if and only if one of the following two happens:
					\begin{enumerate}
						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
					\end{enumerate}

>>>>

				In this section, we will prove theorem \ref{th2}. We will prove it by proving the following theorem:

@@

					Using MILP, if every nodes $b$ in any compensating pair
					$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
					bounds computed by MILP are the exact maximal and minimal value of $z$.
				\end{theorem}

@@

				\begin{lemma} \label{lem:open_node_2}
					A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
					\begin{enumerate}
						\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $W_{b,z}=0$ to denote this case, or
						\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $W_{a_j,b}=0$ to denote this case.
					\end{enumerate}
